### 2021-10-14 paper/pldi22/abstract.tex
First draft of intro

\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in various fields. Recently,
  it has rapidly evolved with a yearly release cadence and open development
  process to adapt users' demands to the language quickly. In this fast-evolving
  nature of JavaScript, the need for \textit{language design assistants} has
  grown to understand the current language semantics and to update it with new
  language features in a tool-based approach. Unfortunately, existing tools have
  two limitations related to the \textit{understanding} and \textit{update} of
  language semantics. They 1) do not provide any automatic ways to focus on
  target semantics and 2) manually or slowly synchronize three language
  components: specifications, conformance tests, and language-based tools.

>>>>

\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in various fields. Recently,
  it has rapidly evolved with a yearly release cadence and open development
  process to adapt users' demands to the language quickly. In this fast-evolving
  nature of JavaScript, the need for \textit{language design assistants} has
  grown to understand the current language semantics and to update it with new
  language features in a tool-oriented approach. Unfortunately, existing tools have
  two limitations related to the \textit{understanding} and \textit{update} of
  language semantics. They 1) do not provide any automatic ways to focus on
  target semantics and 2) manually or slowly synchronize three language
  components: specifications, conformance tests, and language-based tools.

### 2021-10-14 paper/pldi22/intro.tex
First draft of intro

\todo Figure

@@

In this fast-evolving nature of JavaScript, the need for \textit{language design
assistants}~\cite{lda} has grown to understand the current language semantics
and to update it with new language features in a tool-based approach. In the
early 2000s, \citet{lda} first presented the concept of language design
assistants, and several researchers actualized it in tools such as
LISA~\cite{lisa} and $\asfsdf$~\cite{asf-sdf, meta-env}. As described in
Figure~\ref{fig:lda}, they bridge the gap between three language components:
specifications, conformance tests, and language-based tools (e.g., parsers,
interpreters, and compilers) by automatically generating them from the language
semantics. However, only small-size domain-specific languages are their targets
due to their low expressive power. On the other hand, several tools recently
have been presented towards language design assistants for JavaScript in
academia and industry. For example, JSExplain~\cite{jsexplain},
Narcissus~\cite{narcissus}, and engine262~\cite{engine262} are reference
interpreters that closely follow writing styles of ECMAScript, and they provide
debugger-style support. $\jiset$~\cite{jiset} is a tool to compile ECMAScript to
an executable specification. $\jest$~\cite{jest} is an extension of $\jiset$ to
synthesize conformance tests, and $\jstar$~\cite{jstar} is another extension
that performs type analysis for the specification.

However, existing language design assistants for JavaScript have two limitations
related to the \textit{understanding} and \textit{update} of language semantics.
First, they do not provide any automatic ways to focus on target semantics for
better comprehension. JavaScript language designers often want to understand
specific language semantics in the revision process. However, existing tools do
not provide mechanized methods; thus, finding related parts manually in the
specification or conformance tests is tedious. For example, while reference
interpreters and $\jstar$ visualize execution states and type information,
respectively, in the specification, they cannot localize parts in the
specification or conformance tests related to the target semantics. Second, they
manually or slowly synchronize three language components. For example, there is
no synchronization between reference interpreters with other language
components: ECMAScript and conformance tests. While $\jiset$ and $\jest$
automatically generate interpreters and conformance tests from ECMAScript, they
are appropriate for live language design because of the long time to extract
them from scratch for each semantics update.

@@

Our contributions are as follows:
\begin{itemize}
  \item \todo language design assistant for JavaScript with automatic sync
  \item \todo filtering with syntactic views
  \item \todo fast update for live language design
\end{itemize}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{img/lda.png}
  \caption{A manual approach (left) and a tool-oriented approach with language
    design assistants (right) with three language components: specifications,
  conformance tests, and language-based tools.}
  \label{fig:lda}
  \vspace*{-.5em}
\end{figure}

@@

In this fast-evolving nature of JavaScript, the need for \textit{language design
assistants} has grown to understand the current language semantics and to update
it with new language features in a tool-based approach. In the early 2000s,
\citet{lda} first presented the concept of language design assistants, and
several researchers actualized it in tools such as LISA~\cite{lisa} and
$\asfsdf$~\cite{asf-sdf, meta-env}. As described in Figure~\ref{fig:lda}, they
bridge the gap between three language components: specifications, conformance
tests, and language-based tools (e.g., parsers, interpreters, and compilers) by
automatically generating them from the language semantics. Moreover, they
provide query-based interactions to language designers for better understanding.
However, only small-size domain-specific languages are their targets due to
their low expressive power. On the other hand, several tools recently have been
presented towards language design assistants for JavaScript in academia and
industry. For example, JSExplain~\cite{jsexplain}, Narcissus~\cite{narcissus},
and engine262~\cite{engine262} are reference interpreters that closely follow
writing styles of ECMAScript, and they provide debugger-style support.
$\jiset$~\cite{jiset} is a tool to compile ECMAScript to an executable
specification. $\jest$~\cite{jest} is an extension of $\jiset$ to synthesize
conformance tests, and $\jstar$~\cite{jstar} is another extension that performs
type analysis for the specification.

However, existing tools for JavaScript language design assistants have two
limitations related to the \textit{understanding} and \textit{update} of
language semantics. First, they do not provide any automatic ways to focus on
target semantics for better comprehension. JavaScript language designers often
want to understand specific language semantics in the revision process. However,
existing tools do not provide mechanized methods; thus, finding related parts
manually in the specification or conformance tests is tedious. For example,
while reference interpreters and $\jstar$ visualize execution states and type
information, respectively, in the specification, they cannot localize parts in
the specification or conformance tests related to the target semantics. Second,
they manually or slowly synchronize three language components. For example,
there is no synchronization between reference interpreters with other language
components: ECMAScript and conformance tests. While $\jiset$ and $\jest$
automatically generate interpreters and conformance tests from ECMAScript, they
are appropriate for live language design because of the long time to extract
them from scratch for each semantics update.

@@

Our contributions are as follows:
\begin{itemize}
  \item We present $\tool$, a live language design assistant for JavaScript with
    syntactic views. It automatically synchronizes three language components:
    specifications, conformance tests, and language-based tools.
  \item We introduce a way to enhance the understanding of the target semantics
    using user-defined \textit{syntactic views}, abstract syntax trees
    containing abstract nodes. We experimentally demonstrate its effectiveness
    with randomly selected syntactic views.
  \item Towards \textit{live} language designs, we present an approach to detect
    which parts of semantics are revised and partially update related parts in
    language components. We also evaluate how it efficiently propagates
    modification to language components with randomly modified semantics.
\end{itemize}
